---
title: "Turley_Project/HW_02"
author: "sally_turley"
date: "2023-03-02"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
View(Project02_SuperStoreOrders)

superstore <- Project02_SuperStoreOrders

```


## Create a Summary Statistic

```{r super store orders}
summary(superstore)
```
# The data show that the data is clean and does not have an abundance of 
  values which need to be removed. In fact, there are none that I can identify. 
  All of the data has the same length so we are able to manipulate it easily. 
  
  The data ranges from 2011 to 2014 and examines the sales, quantity purchased, 
  discounts recieved, profits earned, shipping costs and the urgency (priority)
  assisgned to the order. 
  
  The data is structured around the order_ID. A new order ID is created for each
  purchase so a single customer can have many order IDs. 
  
  The dates are not in date format and will need to be lubridated. 
  
  
  
  
## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
